Climatic warming strengthens a positive feedback between alpine shrubs and fire (Supplementary Material)

### 2016-03-08 manuscript/supplementary.Rnw
removed period in one section

\section*{Data analysis.}
In total we built 11 hierarchical models to examine factors influencing tussock grass post-fire recovery and shrub seedling establishment, growth and mortality. These models are well suited to datasets that have a hierarchical structure (e.g. plots within sites) because they can account for observation error and partition both explained and unexplained variation at multiple levels of a dataset\cite{Gelman:2007te, Kery:2012wl}. For each model we used Bayesian inference and fitted models with sampling in R \Sexpr{paste(version$major, version$minor, sep='.')} using package Rstan \Sexpr{packageVersion("rstan")}. For each model, three independent chains were executed. In all cases modelled parameters converged within 1000 iterations. Convergence was assessed through both visual inspection of chains and reference to the Brooks-Gelman-Rubin convergence diagnostic\cite{Gelman:1992ts, Brooks:1998ju}. After discarding the first 1000 iterations as ‘warm up’, a further 1000 iterations were taken from the joint posterior. Below we describe the model structure, parameters and priors used in these models. The residuals of all models were checked graphically against predictions with none showing any systematic pattern or severe heteroscedasticity. To ensure all covariate effects were identifiable we selectively removed each covariate and visually inspected whether the direction and magnitude of effects were severely altered; none were. Data and source code for reproducing analysis and figures is available at: \url{https://github.com/jscamac/Alpine_Shrub_Experiment}.

>>>>

\section*{Data analysis}
In total we built 11 hierarchical models to examine factors influencing tussock grass post-fire recovery and shrub seedling establishment, growth and mortality. These models are well suited to datasets that have a hierarchical structure (e.g. plots within sites) because they can account for observation error and partition both explained and unexplained variation at multiple levels of a dataset\cite{Gelman:2007te, Kery:2012wl}. For each model we used Bayesian inference and fitted models with sampling in R \Sexpr{paste(version$major, version$minor, sep='.')} using package Rstan \Sexpr{packageVersion("rstan")}. For each model, three independent chains were executed. In all cases modelled parameters converged within 1000 iterations. Convergence was assessed through both visual inspection of chains and reference to the Brooks-Gelman-Rubin convergence diagnostic\cite{Gelman:1992ts, Brooks:1998ju}. After discarding the first 1000 iterations as ‘warm up’, a further 1000 iterations were taken from the joint posterior. Below we describe the model structure, parameters and priors used in these models. The residuals of all models were checked graphically against predictions with none showing any systematic pattern or severe heteroscedasticity. To ensure all covariate effects were identifiable we selectively removed each covariate and visually inspected whether the direction and magnitude of effects were severely altered; none were. Data and source code for reproducing analysis and figures is available at: \url{https://github.com/jscamac/Alpine_Shrub_Experiment}.
